---
title: "PSP_Clean"
author: ""
date: "30 October 2018"
output: pdf_document
---

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

## R Markdown

R Markdown syntax allows R code, outputs, and figures to be rendered in the documentation.

For help writing in R Markdown, see http://rmarkdown.rstudio.com/.

# Usage

```{r module_usage}
library(SpaDES)

setPaths(modulePath = file.path("C:/Ian/Git/PSP_Clean/modules"))
paths <- list(
  inputPath = "C:/Ian/Git/PSP_Clean/inputs/",
  outputPath = "C:/Ian/Git/PSP_Clean/outputs",
  cachePath = "C:/Ian/Git/PSP_Clean/cache/",
  modulePath = "C:/Ian/Git/PSP_Clean/modules/"
) # shows where the 4 relevant paths are

setPaths(inputPath = paths$inputPath,
         outputPath = paths$outputPath,
         cachePath = paths$cachePath,
         modulePath = paths$modulePath)

getPaths()
times <- list(start = 0, end = 10)

parameters <- list(
  #.progress = list(type = "text", interval = 1), # for a progress bar
  ## If there are further modules, each can have its own set of parameters:
  #module1 = list(param1 = value1, param2 = value2),
  #module2 = list(param1 = value1, param2 = value2)
)
modules <- list("PSP_Clean")
objects <- list()
inputs <- list()
outputs <- list()

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects)

mySimOut <- spades(mySim)
```

```{r}
#Get climate Data
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("PSP_Clean", "path/to/modules/dir")` may be sufficient.

## Output data

Main outputs are allSP (the combined sample plots) and allLocations(combined locations of sample plots). Both datasets have column "MeasureID" which is a unique ID assigned to each plot/sample year combination. Thus the same plot sampled in consecutive years has two different MeasureIDs. There are also "OrigPlotID1" and "OrigPlotID2" which are remnants from the original disparate sample plot datasets. Some datasets had composite keys hence OrigPlotID2, which is NA for those sampe plots that did not.

A second cleaning must preserve only plots that were sampled at least3 times over a period exceeding 10 years (this is the most selective criteria), measured at DBH, with at least 30 trees in the stand. Only trees wider than 10 cm at DBH are used, because the size cut-off for measurement differs by province) 

# Links to other modules

Describe any anticipated linkages to other modules.

